### 2019-07-08 papers/journal/prelim.tex
adde dSMT

QBFs also allow quantifiers over Boolean variables.
%
For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
%
The formula says that for both the values of $x$ there is a value of $y$
such that $x \lor y$ is 1.
%
The problem of finding a satisfying assignment for QBFs is even harder problem~\cite{savitch1970relationships, stockmeyer1973word}.
%

\subsubsection{Solvers}
In this paper, we will encode several problems into finding satisfying solutions of a Boolean formula or QBFs.
%
We will use SAT, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are the result of several decades of research
and implement sophisticated algorithms.
%
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
SMT solvers~\cite{nieuwenhuis2006solving, barrett2018satisfiability} in addition adds supports for some first order theories like arithmetic, arrays etc.
%

The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.

>>>>

The SMT~\cite{barrett2018satisfiability} is a generalization of Boolean satisfiability problem with domain-specific reasoning, for example, support for uninterpreted functions, equality, arithmetic and data structures like arrays, bit-
vectors, etc.
%
For example, $f(f(u,v),v)=f(u,v)$ where $f$ is some unspecified function of two arguments has equality involving uninterpreted terms and function symbols.

%QBFs also allow quantifiers over Boolean variables.
%
The QBF~\cite{buning2009theory, benedetti2008qbf} is a generalization of the Boolean satisfiability problem in which every variable is quantified using either existential or universal quantifier.
%
The QBFs enables potentially more succinct encodings than SAT~\cite{jussila2007compressing} although much more difficult~\cite{savitch1970relationships, stockmeyer1973word} to solve.
For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
%
The formula says that for both the values of $x$ there is a value of $y$
such that $x \lor y$ is 1.
%
%The problem of finding a satisfying assignment for QBFs is even harder problem~\cite{savitch1970relationships, stockmeyer1973word}.
%

\subsubsection{Solvers}
In this paper, we will encode several problems into finding satisfying solutions of a Boolean formula or QBFs.
%
We will use SAT, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are the result of several decades of research
and implement sophisticated algorithms.
%
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
SMT solvers~\cite{nieuwenhuis2006solving, barrett2018satisfiability} in addition adds supports for some first order theories like arithmetic, arrays etc.
% 
The QBF solver adds support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.
%
%We will model the search problem for the universal condition as a QBF~\cite{buning2009theory, benedetti2008qbf}, and the resultant formula is solved using a QBF solver.
%
